%%
%& -job-name=Rosen,Elie-Resume
% LaTeX source of my resume
% =========================
% This file is licensed under the CC-NC-ND Creative Commons license.

% start a document with the here given default font size and paper size
\documentclass[10pt,a4paper]{article}

\pdfpagewidth=8.5in
\pdfpageheight=11in
% include the `tex` instructions that takes care of loading packages and defining commands
\include{resume-commands}

\begin{document} % begin the content of the document
\sloppy % this to relax whitespacing in favour of straight margins

\maintitle{Elie Rosen}{} % title on top of the document
\centerline{\noindent\href{http://www.linkedin.com/in/elierosen}{http://linkedin.com/in/elierosen}}

\nobreakvspace{0.3em} % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:elie@mylifeiscomputers.net}{elie\mbox{}@\mbox{}mylifeiscomputers.net} \hfill Cell: 914.536.2149 \\

\spacedhrule{-0.6em}{-0.4em} % a horizontal line with some vertical spacing before and after

\roottitle{Summary}
	{\bodytext{U.S. citizen with security clearance, looking for full-time work in the areas of ASIC and FPGA front end design. Currently residing near Baltimore, MD and willing to relocate. Primary skills include; System Verilog, VHDL, Clock Domain Crossings, UVM, C/C++/C\#, common scripting languages (Tcl, Python, Perl, UNIX), and protocols (JESD, PCIe, ONFI, GIGE, SFPDP) with a wide range of experience with multiple vendor tools. }}
	
\spacedhrule{0.6em}{-0.4em}

\roottitle{Experience}

	\headedsection % sets the header for the section and includes any subsections
		{\href{http://www.northropgrumman.com/Pages/default.aspx}{Northrop Grumman - Mission Systems}}
		{\textsc{Linthicum Heights, MD}} {%

		\headedsubsection % sets the header for a subsection and contains usually body text
			{ASIC Design and Verification Engineer}
			{July '15 -- Present}
			{\bodytext{ Anti-tamper processing implementation and verification \sbull Experience with ARM architecture, AMBA, and cache design. \sbull Experience with vendor IP integration and verification \sbull Creation of custom scripts to increase team productivity \sbull Designed gate-level verification flow to be used to verify entire design with back annotation \sbull Automated and designed scripts to verify and resolve clock domain crossing issues \sbull Implemented automated LINT checking across design }}

		\headedsubsection % sets the header for a subsection and contains usually body text
			{FPGA Design Engineer}
			{}
			{\bodytext{ Primary integration engineer for a radar system front end processor utilizing Vertex 7 series FPGAs. Implemented a JESD 204B serial RX path \sbull Validated and corrected the DSP pipeline to ensure mathematical correctness \sbull Implemented and designed a coherent SFPDP protocol for transmission of radar samples between panels and the radar processor \sbull Maintained internal registers and documentation accordingly }}

		\headedsubsection % sets the header for a subsection and contains usually body text
			{Internal Professional Activities}
			{}
			{\bodytext{ \begin{itemize}
			    \item High School Innovation Challenge (HSIC) mentor to eight Ft. Meade High School students
			    \item Professional Development Program Navigator to three recently hired engineers
			\end{itemize} }}
	}

	\headedsection % sets the header for the section and includes any subsections
		{\href{http://www.teledynelecroy.com}{Teledyne Lecroy}}
		{\textsc{Chestnut Ridge, NY}} {%

		\headedsubsection % sets the header for a subsection and contains usually body text
			{Digital IC Design Intern}
			{May '14 -- Aug '14}
			{\bodytext{ Designed the digital front-end of a 12-bit Analog/Digital converter for use in mid-range to high-end digital oscilloscopes. Worked with various communication protocols and standards including: SPI, JTAG, and JESD at the hardware implementation level. Implemented UVM test sequences and agents to verify overall system design. Created scripts for increased productivity in Cadence. Maintained accurate and detailed documentation for all completed work. }}
	}

	\headedsection % sets the header for the section and includes any subsections
		{\href{http://www.ece.rutgers.edu/embedded-systems}{Rutgers University Electrical \& Computer Engineering Department}}
		{\textsc{Piscataway, NJ}} {%

		\headedsubsection % sets the header for a subsection and contains usually body text
			{Teaching Assistant}
			{June '13 -- May '15}
			{\bodytext{ {\bf ECE 492/519: Hardware/Software Design of Embedded Systems} \sbull
				Developed the instructional lab for a new course at Rutgers based on the Altera Cyclone series FPGAs that includes topics on Flip-Flops and Latches, Addition Systems, Finite State Machines, ALUs, Ethernet, VGA, Nand Flash, and SRAM. 

			{\bf Expected student outcome}: A complex understanding of FPGAs and their use in industry including advanced knowledge of the 					VHDL hardware description language and proper testing and verification techniques for implementing functional hardware.}}
	}

	\headedsection 
		{\href{http://www.siemens.com}{Siemens Industry, Inc.}}
		{\textsc{Dallas, TX}} {%

	\headedsubsection
		{Electrical and Controls Automation Engineer Intern}
		{May '12 -- Aug '12}
		{\bodytext{Programmed Schneider Modicon Quantum PLC to build 
			\href{http://en.wikipedia.org/wiki/Baggage_handling_system}{Baggage Handling System (BHS)} 
			for\\ Minneapolis St. Paul airport \sbull Designed 
			\href{http://en.wikipedia.org/wiki/Human_machine_interface}{Human Machine Interface (HMI)} 
			used for overview of BHS system health and operator controls \sbull 
			Created tools to generate documentation and test plans from databases with over 10,000 entries \sbull
			Primary presenter of the \href{http://en.wikipedia.org/wiki/Acceptance_testing}
			{Factory Acceptance Test} to client; enabling project to enter the next 
			stage of development }}
}


\spacedhrule{0.6em}{-0.4em}


\roottitle{Education}
\headedsection
{Rutgers, the State University of New Jersey}
{\textsc{New Brunswick, NJ}} {%
\headedsubsection
	{Masters of Science in Computer Engineering \sbull GPA: 3.83/4.00}
	{2013 -- 2015}

	{}
}
\headedsection
{Rutgers, the State University of New Jersey}
{\textsc{New Brunswick, NJ}} {%
\headedsubsection
	{Bachelor of Science in Electrical \& Computer Engineering}
	{2009 -- 2013}
	{\\ {\bf Minor: Entrepreneurship \sbull GPA: 3.17/4.00}}

	{}
}


%\spacedhrule{0.6em}{0em} % a horizontal line with some vertical spacing before and after

%\vspace{5mm}\centerline { 914.536.2149 \emph{(Cell)}  \sbull mylifeiscomputers \emph{(Skype)}  \sbull 1710 Fieldstone Court \sbull Hanover \sbull MD 21076}

\end{document}

